### 2016-11-04 text/ms.Rmd
More copyediting

<!-- It is often important to provide measures of uncertainty with quantitative -->
<!-- estimates. --> 
\R{B}
We illustrated that superensembles can improve point
estimates of status and trends in status; however, there is no reason why
superensembles cannot also be used to
provide measures of uncertainty around those point estimates. 
First, the same approaches to deriving measures of uncertainty from any regression model are available to a superensemble. 
For example, likelihood profile confidence intervals or Bayesian credible intervals 
are available for superensembles fit via maximum likelihood or Bayesian procedures.
Measures of predictive uncertainty can be generated for machine learning
methods such as random forests or GBMs using 
bootstrap procedures [e.g. @hastie2009; @finnegan2015].
Furthermore, uncertainty from the component models could 
be included in superensembles.
These superensembles could be fit using any errors-in-variables or
measurement-error modelling approach [e.g. @carroll2006]

@@

Combining predictions from multiple models via superensemble methods is broadly
useful in other subfields of fisheries science and ecology in general.
Predictions about extinction risk are widely used at the national (e.g., the US
Endangered Species Act and the Canadian Species at Risk Act) and international
[e.g., the IUCN Red List, @iucn2015] levels. These risk assessments generally
involve fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g., @anderson2011a; @pinsky2011], or fitting
population-dynamic models to data for individual species [e.g., @dfo2010]. Both
types of models are prone to error caused by model-misspecification and
therefore results are sensitive to decisions about model structure
[@brooks2015]. Although there are options to account for potential
model-misspecification in determination of species risk [e.g., coefficient
averaging, @burnham2002; generalized modeling, @yeakel2011; or semi-parametric
methods, @thorson2014], ensemble methods are a relatively simple way to combine
predictions in a transparent manner. Beyond estimates of status and trend,
ensemble methods could be used, for example, to increase the robustness of
spatial predictions when designing networks of protected areas
[@rassweiler2014] or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].

\R{A}Superensembles may be able to assist with some longstanding
issues in fisheries science.
For example, superensembles assist by not needing to decide on one model ---
instead of deciding on dome versus asymptotic fisheries 
selectivity [e.g., @sampson2012], 
or on whether to fix or estimate natural mortality [e.g., @johnson2014],
superensembles can use multiple models to draw inference.
Furthermore, the relative contributions of individual models can help tease apart 
the conditions under which various model assumptions 
result in the most accurate predictions.
Finally, superensembles can be used to directly 
estimate other quantities of interest in fisheries science. 
For instance, superensembles could be used to estimate 
fishing mortality compared to fishing mortality at MSY ($F/F_\mathrm{MSY}$)
or a fisheries selectivity curve parameter.
However, superensembles are not a panacea 
and are ultimately limited by the quality, breadth, and representativeness
of simulated or trusted data to which they are calibrated.

>>>>

<!-- It is often important to provide measures of uncertainty with quantitative -->
<!-- estimates. --> 
\R{B}
We illustrated that superensembles can improve point
estimates of population status and trends in status; however, there is no reason why
superensembles cannot also be used to
provide measures of uncertainty around those point estimates. 
The same approaches to deriving measures of uncertainty from any regression model are available to a superensemble. 
For example, likelihood profile confidence intervals or Bayesian credible intervals 
are available for superensembles fit via 
maximum likelihood or Bayesian procedures, respectively.
Measures of predictive uncertainty can be generated for machine learning
methods such as random forests or GBMs using 
bootstrap procedures [e.g. @hastie2009; @finnegan2015].
Furthermore, uncertainty from the component models could 
be included in superensembles.
These superensembles could be fit using any errors-in-variables or
measurement-error modelling approach [e.g. @carroll2006]

@@

Combining predictions from multiple models via superensemble methods is broadly
useful in other subfields of fisheries science and ecology in general.
\R{A}In fisheries science, superensembles provide an 
additional tool to assist with some longstanding issues.
For example, superensembles assist since modelers need not 
decide on one model ---
instead of deciding on dome versus asymptotic fisheries 
selectivity [e.g., @sampson2012], 
or on whether to fix or estimate natural mortality [e.g., @johnson2014],
superensembles can use multiple models to draw inference.
Furthermore, the relative contributions of individual models can help tease apart 
the conditions under which various model assumptions 
result in the most accurate predictions.
Finally, superensembles can be used to directly 
estimate other quantities of interest in fisheries science. 
For instance, superensembles could help assess overfishing by estimating 
fishing mortality compared to fishing mortality at MSY ($F/F_\mathrm{MSY}$)
or be trained to estimate natural mortality.

More broadly, in ecology 
predictions about extinction risk are widely used at national (e.g., the US
Endangered Species Act and the Canadian Species at Risk Act) and international
[e.g., the IUCN Red List, @iucn2015] levels. These risk assessments generally
involve fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g., @anderson2011a; @pinsky2011], or fitting
population-dynamic models to data for individual species [e.g., @dfo2010]. Both
types of models are prone to error caused by model-misspecification and
therefore results are sensitive to decisions about model structure
[@brooks2015]. Although there are options to account for potential
model-misspecification in determination of species risk [e.g., coefficient
averaging, @burnham2002; generalized modeling, @yeakel2011; or semi-parametric
methods, @thorson2014], ensemble methods are a relatively simple way to combine
predictions in a transparent manner. Beyond estimates of status and trend,
ensemble methods could be used, for example, to increase the robustness of
spatial predictions when designing networks of protected areas
[@rassweiler2014] or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].
In any case, superensembles are not a panacea 
and are ultimately limited by the quality, breadth, and representativeness
of simulated or trusted data to which they are calibrated.
